Data Analysis

### 2022-08-26 04.manuscript_scopus.Rmd
adding outline

science collaboration overall 
  - what is collaboration
  - is it increasing 
  - globalization should help

rise of big team science because the need for resources, replication, reproducibility, generalization  
  - physics
  - biology 
  - psychology

metascience
  - most research is on lessons learned, why bts is useful
  - little research on who/fields has done bts
  - has the globalization of science actually impacted people other than NA and Europe

>>>>

science collaboration overall (sav)
  - what is collaboration
  - is it increasing 
  - globalization should help

rise of big team science because the need for resources, replication, reproducibility, generalization (erin)
  - physics
  - biology 
  - psychology

metascience (erin)
  - most research is on lessons learned, why bts is useful
  - little research on who/fields has done bts
  - has the globalization of science actually impacted people other than NA and Europe

about this project paragraph (erin)
